Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-16 ms.tex
Start on the new appendix.
Modifying the mdot_mass figure.

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the
  black hole accretion rate $\dot{M}$ in Eddington units as a function
  of black hole mass $M_{\bullet}$, shown separately for core
  ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$,
  dot-dashed lines).  Black lines show the accretion rate calculated
  from equation (\ref{eq:eddr_analytic}) using our estimate of the gas
  heating rate provided at $z = 0$ by the average star formation
  histories for each galaxy mass (Fig.~\ref{fig:vwSources}).  Green
  lines show the maximum accretion set by Ia supernovae blow-out
  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate so obtained
  if Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).  Yellow
  lines show the maximum accretion rate for a thermally stable flow
  near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  We also show
  Eddington ratios inferred for the galactic center from
  \citet{Quataert:2004a} (black circle) and for NGC3115 from
  \citet{ShcherbakovWong+:2014a} (black diamonds).  {\bf BDM: turn quataert/sch into lines, add J1644+57 lines extending below 1e7 msun} {\it Bottom
    panel:} Growth times $\Mbh/\Mdot$ in units of the Hubble time
  $\th$ for each of the accretion rates shown in the top panel.}
\end{figure}

@@

  \clearpage
  \appendix
  \section{Analytic Expression for the stagnation radius}
  \label{app:rs}
  \input{rs}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the
  black hole accretion rate $\dot{M}$ in Eddington units as a function
  of black hole mass $M_{\bullet}$, shown separately for core
  ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$,
  dot-dashed lines).  Black lines show the accretion rate calculated
  from equation (\ref{eq:eddr_analytic}) using our estimate of the gas
  heating rate provided at $z = 0$ by the average star formation
  histories for each galaxy mass (Fig.~\ref{fig:vwSources}).  Green
  lines show the maximum accretion set by Ia supernovae blow-out
  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate so obtained
  if Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).  Yellow
  lines show the maximum accretion rate for a thermally stable flow
  near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  We also show
  Eddington ratios inferred for the galactic center from
  \citet{Quataert:2004a} (line with black circle) and for NGC3115 from
  \citet{ShcherbakovWong+:2014a} (line with black diamonds) and for
  the Swift J1644+57 event from \citet{BergerZauderer+:2012a} (line
  with black crosses) {\it Bottom panel:} Growth times $\Mbh/\Mdot$
  in units of the Hubble time $\th$ for each of the accretion rates
  shown in the top panel.}
\end{figure}

@@

  \clearpage
  \appendix
  \section{Analytic expression for the stagnation radius}
  \label{app:rs}
  \input{rs}

  \section{Analytic expression for specific enthalpy of gas}
  {\bf AG: double check that what we are deriving here is actually
    specific enthalpy}
  \label{app:be}
  \input{be}
